Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-06-03 paper_jasa.tex
experiment1 details

Each subject viewed 10 lineups. Selection of lineups shown to each subject followed these rules .... \green{fill this in}. Figure \ref{fig:test_category} is an example of one of these lineups. The visual test statistic is a side-by-side boxplot.

>>>>

{\bf Number of evaluations} required for each lineup is determined based on the precision level of the estimated power. Suppose $\gamma$ denotes the classical UMP test power for each parameter combination shown in table \ref{tbl:experiment_params}. Since expected power of visual inference is very close to the power of classical UMP test as in figure \ref{fig:power_expected} the proportion of successful evaluations of lineups should give a rough estimate for  $\gamma$. For a given proportion $\gamma$ we want to have margin of error (ME) to be 0.1. Thus we have $ME =1.96 \sqrt{ \frac 1 n_{\gamma} \gamma(1-\gamma)} \le 0.05$ which gives us the estimation of minimum number of evaluations $$n_{\gamma} \geq \frac{\gamma(1-\gamma)}{(0.05/1.96)^2}.$$  
Each subject viewed at least 10 lineups and we allowed them to provide more evaluations if they wanted. Depending on the parameter combinations we group the lineups in different difficulty levels such as easy, medium, hard and mixed as shown in table \ref{tbl:dist_lineup1}. For each difficulty level a specific number of lineups were randomly picked to show for evaluation. This number is chosen so that total number of evaluations for each lineup for that group exceed the threshold $n_{\gamma}$. To satisfy this plan we needed to recruit at least 300 subjects.

%For a given proportion $p$ we want to have margin of error (ME) to be 0.1. Thus we have $ME =1.96 \sqrt{ \frac 1 n p(1-p)} \le 0.05$ which gives us the estimation of minimum number of evaluations $$n_p \geq \frac{p(1-p)}{(0.05/1.96)^2}.$$ Now from the theoretical (UMP) power curve for each parameter combinations shown in table \ref{tbl:experiment_params} we know the power(say $p$) and thus we can estimate the number of evaluations required for that specific combinations of parameter. We collect data such that each of the parameter combinations in the table \ref{tbl:experiment_params} has approximately the estimated sample size that we calculated here.
  Figure \ref{fig:test_category} is an example of one of these lineups. The visual test statistic is a side-by-side boxplot.

\begin{table}[hbtp]
\caption{Selection of 10 lineups for a person to evaluate in the simulation experiment with discrete covariate described in section \ref{sec:category}.} 
\centering
\begin{tabular}{c c c c  c c c}
\hline\hline
Difficulty& \multicolumn{3}{c}{parameter combination}& Number of evaluations &Total number  & number of lineups\\
level & $n$ & $\sigma$ & $\beta$ &required($n_{\gamma}$) & of lineups & randomly shown \\
\hline
easy&100& 5&8 & 1& 12 & 1\\
&100&12&16 &1&&\\
&300& 5&5 &1&&\\
&300&12&10 &1 &&\\
\hline
medium&100& 5&3 &203 & 9 &2\\
&300& 5&2,3 & 97, 1&&\\
\hline
hard&100&12&3,8,10 & 277, 126, 23& 18 &6\\
&300& 5&1 & 371 &&\\
&300&12&3,5& 375,74 &&\\
\hline
mixed&100& 5&1,5,0& 214, 2,73 & 21 &1\\
&100&12&1& 100& &\\
&300& 5&0 & 73&&\\
&300&12&7,1& 2, 152&&\\
\hline
Total &&&&&60&10\\
\hline
\end{tabular}
\label{tbl:dist_lineup1}
\end{table}
